Active Learning for SAT Solver Benchmarking

### 2023-01-12 paper/paper.tex
Include ORCID icons
According to camera-ready instructions, authors should do this themselves.

\usepackage[ruled,vlined,linesnumbered,norelsize]{algorithm2e}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc} % font encoding; recommended by LNCS template
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[misc]{ifsym} % letter symbol to mark corresponding author
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{tikz} % has to be loaded after "xcolor" here, else "option clash"

@@

\author{
  Tobias Fuchs\orcidID{0000-0001-9727-2878} (\Letter) \and \\
  Jakob Bach\orcidID{0000-0003-0301-2798} \and \\
  Markus Iser\orcidID{0000-0003-2904-232X}
  %JB: according to camera-ready mail, we might need to include ORCID logo and link ourselves; there is a package called "orcidlink" for that purpose
}

>>>>

\usepackage[ruled,vlined,linesnumbered,norelsize]{algorithm2e}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc} % font encoding; recommended by LNCS template
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[misc]{ifsym} % letter symbol to mark corresponding author
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{orcidlink} % ORCID icon and link; has to be loaded after "xcolor" here, else "option clash"; class "llncs" also has command "\orcidID" (which only displays full ID), but camera-ready instructions state you should add icon and link yourself
\usepackage{tikz} % has to be loaded after "xcolor" here, else "option clash"

@@

\author{
  Tobias Fuchs~\orcidlink{0000-0001-9727-2878} (\Letter) \and
  Jakob Bach~\orcidlink{0000-0003-0301-2798} \and
  Markus Iser~\orcidlink{0000-0003-2904-232X}
}
